The \dealii{} Library, Version 8.5

### 2017-03-03 8.5/paper.tex
List major changes.

The major changes of this release are:
\begin{itemize}
\item CellDataStorage class

\item MappingManifold

@@

\item step-57, step-55, step-56

\item step-44 improvements

\item step-37 parallel improvements

\item New code gallery codes demonstrating (i) quasi-static visco-elastic
  material behavior, (ii) multiphase Navier-Stokes flow, (iii) the
  evolution of global-scale topography on planetary bodies, (iv)
  goal-oriented elastoplasticity.

>>>>

The major changes of this release are:
\marginpar{Add one sentence to each of the following.}
\begin{itemize}
\item CellDataStorage class

\item The \texttt{MappingManifold} class provides mappings between the
  reference cell and a mesh cell that is ``exact'' in the sense that
  the edges, faces, and the interior of the mesh cell matches an
  underlying manifold. This is opposed to using the usual polynomial
  approximations of the manifold.

@@

\item New tutorial programs step-55, step-56, and step-57,
  demonstrating parallel solvers for the Stokes equations, a multigrid
  method for the Stokes equation, and methods for the nonlinear
  Navier-Stokes equations, respectively. In addition, the step-37
  tutorial program has been rewritten to support parallel
  computations, and the step-44 tutorial now uses the facilities of
  the physics module mentioned above.

\item New code gallery programs demonstrating (i) quasi-static
  visco-elastic material behavior, (ii) multiphase Navier-Stokes flow,
  (iii) the evolution of global-scale topography on planetary bodies,
  (iv) goal-oriented elastoplasticity.
